---
title: "ESG Content Analysis on US companies"
author: "QTA group 2"
date: "5/19/2021"
output: html_document
---
## Table of Content (temporary)
**Introduction**

**Sample selection and data**

**Research question**

**Readability and the nature of 10K fillings**

**Correspondence**

**Collocation Analysis**

**Applied dictionaries**

**Relative ESG-wording**

**Comparison with ESG-Ratings**

**Trends between industries**

**Limitations**

```{r Loading packages and load/prepare 10Ks, include=FALSE}
# load packages
library(readtext)
library(dplyr)
library(here)
library(readxl)
library(quanteda)
library(stringr)
library(tidyverse)
library(plotly)

# load excel files with cik numbers for each industry with the companies
fashion <- read_excel(here("companies", "fashion_cik.xlsx"), sheet = "Sheet1", col_names = TRUE)
# energy <- read_excel()
# industry3 <- read_excel()

# keeping only the cik number
fashion_cik <- fashion[,13]
# energy_cik <- energy[,13]
# industry3_cik <- industry3[,13]

# load the 10Ks from downloaded files

fashion_10k <- NULL
energy_10k <- NULL
industry3_10k <- NULL

# loop that collects all reports for all companies for each industry
# this will take some minutes!!!

# fashion (should be 436 observations)
for (i in fashion_cik$CIK) {
  output <- readtext(here("Edgar filings_HTML view", "Form 10-K", i))
  fashion_10k <- rbind(fashion_10k, output)
}

# energy
for (i in energy_cik$CIK) {
  output <- readtext(here("Edgar filings_HTML view", "Form 10-K", i))
  fashion_10k <- rbind(all, output)
}

# industry3
for (i in industry_cik$CIK) {
  output <- readtext(here("Edgar filings_HTML view", "Form 10-K", i))
  fashion_10k <- rbind(all, output)
}

# simple cleaning
fashion_10k$text <- str_remove_all(fashion_10k$text, "\n•")
fashion_10k$text <- str_remove_all(fashion_10k$text, "\n")
#energy_10k
#industry3

# define columns into cik, report type and report year
fashion_10k <- separate(
  fashion_10k,
  1,
  into = c("cik", "type", "year", NA),
  sep = "_",
  remove = TRUE)

#energy
#industry3

# only keep year
#keep the year and not the full date
fashion_10k <- separate(
  fashion_10k,
  "year",
  into = c("year", NA),
  sep = "-",
  remove = TRUE)

#energy
#industry3
```


**Introduction**

**Sample selection and data**
We took the 10K filings back to the year 2004. This leads to 18 reports if the on from 2021 was already made public.For the fashion industry we have a average of `r round(ndoc(fashion_10k)/length(unique(fashion_10k$cik)), digits = 2)` total 10K filings per company. This is due to some later SEC registrations after 2004 for some companies.

**Research question**

**Readability and the nature of 10K fillings**
```{r creating a corpus, include=FALSE}
fashion_corp <- corpus(fashion_10k)
#energy
#industry3
```


**Correspondence**

**Collocation Analysis**

**Applied dictionaries**

**Relative ESG-wording**

**Comparison with ESG-Ratings**

**Trends between industries**

**Limitations**
